Conflict-Free Vertex Coloring of Planar Graphs

### 2017-04-10 presentation/presentation.tex
Adding line highlighting for algorithm presentation

\makeatletter
\newcommand{\algcolor}[2]{%
  \hskip-\ALG@thistlm\colorbox{#1}{\raisebox{0pt}[0.1cm][0cm]{\parbox{\dimexpr\linewidth-2\fboxsep}{\hskip\ALG@thistlm\relax #2}}}%
}
\newcommand{\algemph}[1]{\algcolor{Yellow}{#1}}
\makeatother

@@

    \only<2>{
      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State \algemph{$i \gets 1$}
            \State \algemph{Remove all isolated paths from $G$}
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \State Pick any vertex $v$
                \State $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

@@

      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State \algemph{$D \gets \emptyset$}
              \ForAll{components of $G$}
                \State Pick any vertex $v$
                \State $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

@@

      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \State \algemph{Pick any vertex $v$}
                \State \algemph{$D \gets D \cup \{ v \}$}
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1-slide-1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

@@

      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \State Pick any vertex $v$}
                \State $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1-slide-1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

>>>>

% \makeatletter
% \newcommand{\algcolor}[2]{%
%   \hskip-\ALG@thistlm\colorbox{#1}{\raisebox{0pt}[0.1cm][0cm]{\parbox{\dimexpr\linewidth-2\fboxsep}{\hskip\ALG@thistlm\relax #2}}}%
% }
% \newcommand{\algemph}[1]{\algcolor{Yellow}{#1}}
% \makeatother

\usepackage{tikz}
\usetikzlibrary{calc}

\makeatletter
% code borrowed from Andrew Stacey; See
% http://tex.stackexchange.com/a/50054/3954
\tikzset{%
  remember picture with id/.style={%
    remember picture,
    overlay,
    save picture id=#1,
  },
  save picture id/.code={%
    \edef\pgf@temp{#1}%
    \immediate\write\pgfutil@auxout{%
      \noexpand\savepointas{\pgf@temp}{\pgfpictureid}}%
  },
  if picture id/.code args={#1#2#3}{%
    \@ifundefined{save@pt@#1}{%
      \pgfkeysalso{#3}%
    }{
      \pgfkeysalso{#2}%
    }
  }
}

\def\savepointas#1#2{%
  \expandafter\gdef\csname save@pt@#1\endcsname{#2}%
}

\def\tmk@labeldef#1,#2\@nil{%
  \def\tmk@label{#1}%
  \def\tmk@def{#2}%
}

\tikzdeclarecoordinatesystem{pic}{%
  \pgfutil@in@,{#1}%
  \ifpgfutil@in@%
    \tmk@labeldef#1\@nil
  \else
    \tmk@labeldef#1,(0pt,0pt)\@nil
  \fi
  \@ifundefined{save@pt@\tmk@label}{%
    \tikz@scan@one@point\pgfutil@firstofone\tmk@def
  }{%
  \pgfsys@getposition{\csname save@pt@\tmk@label\endcsname}\save@orig@pic%
  \pgfsys@getposition{\pgfpictureid}\save@this@pic%
  \pgf@process{\pgfpointorigin\save@this@pic}%
  \pgf@xa=\pgf@x
  \pgf@ya=\pgf@y
  \pgf@process{\pgfpointorigin\save@orig@pic}%
  \advance\pgf@x by -\pgf@xa
  \advance\pgf@y by -\pgf@ya
  }%
}

\makeatother
% end of Andrew's code

% main command to draw the colored background
\newcounter{mymark}
\newcommand\ColorLine{%
  \stepcounter{mymark}%
  \tikz[remember picture with id=mark-\themymark,overlay] {;}%
  \begin{tikzpicture}[remember picture,overlay]%
    \filldraw[Yellow]%
   let \p1=(pic cs:mark-\themymark),
   \p2=(current page.east)  in
   ([xshift=-0.3em,yshift=-0.7ex]0,\y1)  rectangle ++([xshift=-8.26cm]\x2,\baselineskip);
  \end{tikzpicture}%
}%

% colored loops and declarations
\makeatletter
\algnewcommand\CREQUIRE{\item[\ColorLine\algorithmicrequire]}%
\algnewcommand\CENSURE{\item[\ColorLine\algorithmicensure]}%
\algnewcommand\CSTATE{\State\ColorLine}%
\algnewcommand\CSTATEx{\Statex\ColorLine}%
\algnewcommand\CCOMMENT{\Comment\ColorLine}%

% \algdef{SE}[WHILE]{CWhile}{EndWhile}%
%    [2][default]{\ColorLine\algorithmicwhile\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%
%    {\algorithmicend\ \algorithmicwhile}%
 \algdef{SE}[WHILE]{CWhile}{EndWhile}[1]{\ColorLine\algorithmicwhile\ #1\ \algorithmicdo}{\algorithmicend\ \algorithmicwhile}%

\algdef{SE}[FOR]{CFOR}{ENDFOR}%
   [2][default]{\ColorLine\algorithmicfor\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%
   {\algorithmicend\ \algorithmicfor}%
\algdef{S}[FOR]{CFORALL}%
   [2][default]{\ColorLine\algorithmicforall\ #2\ \algorithmicdo\ALG@compatcomm{#1}}%
\algdef{SE}[LOOP]{CLOOP}{ENDLOOP}%
   [1][default]{\ColorLine\algorithmicloop\ALG@compatcomm{#1}}%
   {\algorithmicend\ \algorithmicloop}%
\algdef{SE}[REPEAT]{CREPEAT}{UNTIL}%
   [1][default]{\ColorLine\algorithmicrepeat\ALG@compatcomm{#1}}%
   [1]{\algorithmicuntil\ #1}%
\algdef{SE}[IF]{CIF}{ENDIF}%
   [2][default]{\ColorLine\algorithmicif\ #2\ \algorithmicthen\ALG@compatcomm{#1}}%
   {\algorithmicend\ \algorithmicif}%
\algdef{C}[IF]{IF}{CELSIF}%
   [2][default]{\ColorLine\algorithmicelse\ \algorithmicif\ #2\ \algorithmicthen\ALG@compatcomm{#1}}%
\algdef{Ce}[ELSE]{IF}{CELSE}{ENDIF}%
   [1][default]{\ColorLine\algorithmicelse\ALG@compatcomm{#1}}%
\makeatother
\algtext*{EndWhile}%

@@

    \only<2>{
      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \CSTATE $i \gets 1$
            \CSTATE Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \State Pick any vertex $v$
                \State $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

@@

      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \CSTATE $D \gets \emptyset$
              \ForAll{components of $G$}
                \State Pick any vertex $v$
                \State $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

@@

      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \CSTATE Pick any vertex $v$
                \CSTATE $D \gets D \cup \{ v \}$
                \While{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1-slide-1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }

@@

      \begin{columns}
        \begin{column}{0.5\textwidth}
          \begin{algorithm}[H]
            \caption*{\textbf{Algorithm} IEDS}
            \scriptsize
            \begin{algorithmic}[1]
            \State $i \gets 1$
            \State Remove all isolated paths from $G$
            \While{$G$ is not empty}
              \State $D \gets \emptyset$
              \ForAll{components of $G$}
                \State Pick any vertex $v$
                \State $D \gets D \cup \{ v \}$
                \CWhile{$\exists u$ at distance $\geq 3$ $\forall v \in D$}
                  \State Pick $u$ at distance 3 from some vertex in $D$
                  \State $D \gets D \cup \{ w \}$
                \EndWhile
                \ForAll{$u \in D$}
                  \State Color $u$ with color $i$
                \EndFor
                \State $i \gets i + 1$
                \ForAll{$u \in D$}
                  \State Remove $N(u)$ from $G$
                \EndFor
                \State Remove all isolated paths from G
              \EndFor
            \EndWhile
            \State Color all removed isolated paths using color $i$
            \end{algorithmic}
          \end{algorithm}
        \end{column}
        \begin{column}{0.5\textwidth}
          \begin{center}
            \begin{textblock*}{8cm}(8cm, 2cm) % {block width} (coords)
              \begin{figure}
                \centering
                \includegraphics[width=6cm]{../figures/algorithm1-slide-1.pdf}
                \caption*{A simple, undirected graph $G$}
              \end{figure}
            \end{textblock*}
          \end{center}
        \end{column}
      \end{columns}
    }
